---
title: "Week 1: Introduction to Machine Learning for Marketing"
subtitle: "Hands-On Lab — TMWR Chapters 1, 3, and 5"
author: "Jae Jung"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: right-body
    toc-float: true
    number-sections: true
    theme: cosmo
    code-fold: false
    code-tools: true
    link-external-newwindow: true
    df-print: paged
    embed-resources: true
execute:
  echo: true
  warning: false
  message: false
---

# Overview

This document accompanies Week 1 of IBM 6540. It covers the key ideas and hands-on coding from three chapters of *Tidy Modeling with R* (TMWR):

-   **Chapter 1** — Software for Modeling: what models are, why tidymodels exists
-   **Chapter 3** — A Review of R Modeling Fundamentals: base R modeling, the formula interface
-   **Chapter 5** — Spending Our Data: train/test splits, stratification, the data budget

By the end of this lab, you should be able to:

1.  Describe the three types of models (descriptive, inferential, predictive)
2.  Fit a model using base R syntax and interpret its output with tidy tools
3.  Split a dataset into training and testing sets using `rsample`
4.  Explain why the data budget matters and when to use stratified splits

------------------------------------------------------------------------

# Setup

## Install and load packages

If you have not yet installed tidymodels, run the install line once (it is commented out below so it does not run every time you render):

```{r}
#| label: install
# Run once if needed:
# install.packages("tidymodels")
# install.packages("broom")
# install.packages("janitor")

library(tidymodels) # loads rsample, parsnip, recipes, workflows, yardstick, broom
library(tidyverse) # loads dplyr, ggplot2, tidyr, readr, etc.

install.packages("conflicted") # for checking function conflicts
library(conflicted)
conflict_prefer("filter", winner = "dplyr") # ensure we are using dplyr's filter, not stats::filter
tidymodels_prefer(quiet = FALSE)
```

Verify your tidymodels version:

```{r}
#| label: version-check
packageVersion("tidymodels")

```

------------------------------------------------------------------------

# TMWR Chapter 1 — Software for Modeling

## Types of models

TMWR Chapter 1 introduces a useful taxonomy. Before writing any code, it is worth asking: **what kind of model are we building, and why?**

| Type | Goal | Example |
|---------------------|---------------------|-------------------------------|
| **Descriptive** | Illustrate or summarize data | Trend line on a chart |
| **Inferential** | Test a hypothesis, estimate an effect | Does ad spend cause sales? |
| **Predictive** | Generate accurate predictions for new data | Which customers will churn? |

In this course, we focus on **predictive models** — but good predictive modeling still requires understanding your data descriptively and sometimes thinking carefully about inference.

## The modeling process

TMWR describes modeling as an **iterative process**, not a one-shot task:

```         
Exploratory data analysis
        ↓
Feature engineering
        ↓
Model fitting
        ↓
Model evaluation
        ↓
Refine (repeat as needed)
        ↓
Final model on test data
```

::: callout-important
**Key principle from Chapter 1:** The test set should be used **only once** — at the very end — to get an honest estimate of how well the model generalizes. Every other evaluation should use the training data only.
:::

## Why tidymodels?

### Data

```{r}
#| label: why-tidymodels-data

# reading data
ames # Ames housing dataset in modeldata
data(ames) # load the dataset
glimpse(ames)
dim(ames)
library(janitor)
ames_train <- ames |> 
  slice(1:1000) |> 
  clean_names() 
```

Before tidymodels, every modeling package in R had its own syntax, its own way of making predictions, and its own output format. Compare:

```{r}
#| label: why-tidymodels
#| eval: false
# Base R linear model
lm(sale_price ~ gr_liv_area, data = ames_train) |> 
  summary()

# randomForest package
install.packages("randomForest")
library(randomForest)
randomForest(sale_price ~ gr_liv_area, data = ames_train) 

# glmnet package (requires matrix input, not a formula)
#install.packages("glmnet")
library(glmnet)
glmnet(x = model.matrix(~gr_liv_area, ames_train), y = ames_train$sale_price)
```

Every package has different syntax, different prediction functions, and different output structures. tidymodels solves this by providing a **unified interface** regardless of the underlying algorithm.

------------------------------------------------------------------------

# TMWR Chapter 3 — R Modeling Fundamentals

## The formula interface

The `~` (tilde) operator is central to modeling in R. It creates a **formula** that separates the outcome from the predictors:

```         
outcome ~ predictor1 + predictor2 + predictor3
```

Let's explore this with the built-in `mtcars` dataset as a warm-up before moving to marketing data.

```{r}
#| label: formula-basics
# Look at the data
glimpse(mtcars)
```

```{r}
#| label: simple-lm
# Fit a simple linear regression using base R
mpg_fit <- lm(mpg ~ wt + hp + cyl, data = mtcars)

# The default summary
summary(mpg_fit)
```

Notice that `summary()` gives us a lot of output, but it is not easy to work with programmatically — the output is printed text, not a tidy data frame.

## Tidying model output with `broom`

The `broom` package (included in tidymodels) solves this. It provides three functions that turn model output into tidy tibbles:

| Function    | What it returns                                 |
|-------------|-------------------------------------------------|
| `tidy()`    | Coefficient-level statistics                    |
| `glance()`  | Model-level statistics (R², AIC, etc.)          |
| `augment()` | Row-level statistics (fitted values, residuals) |

```{r}
#| label: broom-tidy
# Coefficient-level output
tidy(mpg_fit)
```

```{r}
#| label: broom-glance
# Model-level output
glance(mpg_fit)
```

```{r}
#| label: broom-augment
# Row-level output: fitted values and residuals
augment(mpg_fit) |>
  select(mpg, .fitted, .resid) |>
  head(10)
```

::: callout-tip
`tidy()`, `glance()`, and `augment()` work on many model types — not just `lm()`. This is one of the core benefits of the tidymodels ecosystem.
:::

## The formula interface — more options

The formula interface has powerful shorthand:

```{r}
#| label: formula-options
#| eval: false
# Include all predictors
lm(mpg ~ ., data = mtcars)

# Exclude one predictor
lm(mpg ~ . - carb, data = mtcars)

# Interaction term
lm(mpg ~ wt * hp, data = mtcars) # includes wt, hp, and wt:hp

# Explicit interaction only
lm(mpg ~ wt + hp + wt:hp, data = mtcars)

lm(mpg ~ (wt + hp)^2, data = mtcars) 

# interaction only, no main effects
lm(mpg ~ wt:hp, data = mtcars) 

# Polynomial term
lm(mpg ~ wt + I(wt^2), data = mtcars) |> summary()

# Log transformation of predictor
lm(mpg ~ log(wt) + hp, data = mtcars) |> summary()
```

## ✏️ Practice 3.1 — Explore base R modeling

Use the `mtcars` dataset to answer these questions:

```{r}
#| label: practice-3-1
# 1. Fit a model predicting mpg from wt alone
fit_simple <- lm(mpg ~ wt, data = mtcars)

# Use tidy() to see the coefficients
tidy(fit_simple)
```

```{r}
#| label: practice-3-1b
# 2. Use glance() to check model fit
glance(fit_simple)
```

```{r}
#| label: practice-3-1c
# 3. Plot fitted values vs. residuals
augment(fit_simple) |>
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point(color = "#005030", alpha = 0.7) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#FFB81C") +
  labs(
    title = "Fitted Values vs. Residuals",
    x = "Fitted values",
    y = "Residuals"
  ) +
  theme_minimal()
```

::: callout-note
**Your turn:** Try adding `hp` and `cyl` to the model. Does R² improve? Does the residual plot look better or worse? What does that tell you?
:::

## A marketing dataset — customer churn

Let's switch from `mtcars` to a more relevant marketing dataset. We will simulate a customer dataset that mirrors the kinds of data you would encounter in practice:

```{r}
#| label: create-customer-data
set.seed(42)
n <- 1000

customer_data <- tibble(
  customer_id = 1:n,
  tenure = sample(1:60, n, replace = TRUE),
  monthly_spend = round(rnorm(n, mean = 85, sd = 25), 2),
  num_products = sample(
    1:5,
    n,
    replace = TRUE,
    prob = c(0.3, 0.3, 0.2, 0.1, 0.1)
  ),
  num_complaints = rpois(n, lambda = 0.5),
  last_login_days = sample(1:90, n, replace = TRUE),
  region = sample(c("West", "East", "South", "Midwest"), n, replace = TRUE),
  churn = factor(
    ifelse(
      0.05 *
        num_complaints +
        0.02 * last_login_days -
        0.015 * tenure -
        0.005 * monthly_spend +
        rnorm(n, 0, 0.5) >
        0.3,
      "yes",
      "no"
    )
  )
)

glimpse(customer_data)
```

```{r}
#| label: churn-rate
# Check overall churn rate
customer_data |>
  count(churn) |>
  mutate(pct = n / sum(n) * 100)
```

## ✏️ Practice 3.2 — Fit a model on marketing data

```{r}
#| label: practice-3-2a
# 1. Fit a linear model predicting monthly_spend from tenure and num_products
spend_fit <- lm(
  monthly_spend ~ tenure + num_products + region,
  data = customer_data
)

tidy(spend_fit)
```

```{r}
#| label: practice-3-2b
# 2. Check model quality
glance(spend_fit)
```

```{r}
#| label: practice-3-2c
# 3. Visualize residuals
augment(spend_fit) |>
  ggplot(aes(x = .fitted, y = .resid)) +
  geom_point(alpha = 0.3, color = "#005030") +
  geom_hline(yintercept = 0, linetype = "dashed", color = "#FFB81C") +
  labs(
    title = "Residuals: Monthly Spend Model",
    x = "Fitted values ($)",
    y = "Residuals"
  ) +
  theme_minimal()
```

::: callout-note
**Your turn:** Add `num_complaints` and `last_login_days` as predictors. What happens to R²? Does every predictor appear significant? What might this tell you about the data generating process we used to simulate the data?
:::

------------------------------------------------------------------------

# TMWR Chapter 5 — Spending Our Data

## The data budget concept

Chapter 5 introduces one of the most important ideas in applied ML:

> *We have a finite amount of data. Every time we use data to make a modeling decision, we "spend" some of its ability to give us unbiased estimates.*

The solution is to **split the data** before doing any modeling:

-   **Training set** — used for everything: exploration, feature engineering, model fitting, hyperparameter tuning
-   **Test set** — used **once**, at the very end, to estimate real-world performance

```{r}
#| label: split-diagram
#| echo: false
tibble(
  Set = c("Training (~80%)", "Testing (~20%)"),
  Purpose = c(
    "Fit model, tune parameters, make preprocessing decisions",
    "Final honest estimate of model performance — used once"
  ),
  Size = c("800 rows", "200 rows")
) |>
  knitr::kable(caption = "Data budget for our 1,000-row customer dataset")
```

## Basic train/test split with `rsample`

The `rsample` package (part of tidymodels) makes splitting straightforward:

```{r}
#| label: basic-split
library(rsample)

set.seed(123) # Always set a seed for reproducibility

# 80% training, 20% testing
customer_split <- initial_split(customer_data, prop = 0.80)

customer_split
```

```{r}
#| label: extract-sets
# Extract the training and testing sets
customer_train <- training(customer_split)
customer_test <- testing(customer_split)

# Verify sizes
cat("Training rows:", nrow(customer_train), "\n")
cat("Testing rows: ", nrow(customer_test), "\n")
cat("Total:        ", nrow(customer_train) + nrow(customer_test), "\n")
```

## Stratified splitting

Our churn variable is **imbalanced** — only about 20% of customers churn. A random split might give us very different churn rates in training vs. testing.

First, let's see what happens without stratification:

```{r}
#| label: unstratified-check
set.seed(123)

# Without stratification
split_no_strata <- initial_split(customer_data, prop = 0.80)
train_no_strata <- training(split_no_strata)
test_no_strata <- testing(split_no_strata)

cat("Churn rate in full data:\n")
customer_data |> count(churn) |> mutate(pct = round(n / sum(n) * 100, 1))
```

```{r}
#| label: unstratified-check2
cat("Churn rate in training (no strata):\n")
train_no_strata |> count(churn) |> mutate(pct = round(n / sum(n) * 100, 1))
```

```{r}
#| label: unstratified-check3
cat("Churn rate in testing (no strata):\n")
test_no_strata |> count(churn) |> mutate(pct = round(n / sum(n) * 100, 1))
```

Now with stratification:

```{r}
#| label: stratified-split
set.seed(123)

# With stratification on the outcome variable
customer_split_strat <- initial_split(
  customer_data,
  prop = 0.80,
  strata = churn
) # key argument

customer_train <- training(customer_split_strat)
customer_test <- testing(customer_split_strat)

cat("Churn rate in training (stratified):\n")
customer_train |> count(churn) |> mutate(pct = round(n / sum(n) * 100, 1))
```

```{r}
#| label: stratified-split2
cat("Churn rate in testing (stratified):\n")
customer_test |> count(churn) |> mutate(pct = round(n / sum(n) * 100, 1))
```

::: callout-tip
**Rule of thumb:** Always use `strata =` when your outcome is a category with imbalanced classes (e.g. churn, conversion, fraud). For regression outcomes, stratification is less critical but can still help ensure consistent distributions.
:::

## Visualizing the split

It is good practice to verify that your training and testing sets have similar distributions for key variables:

```{r}
#| label: split-viz
# Compare distributions of monthly_spend across splits
bind_rows(
  customer_train |> mutate(set = "Training"),
  customer_test |> mutate(set = "Testing")
) |>
  ggplot(aes(x = monthly_spend, fill = set)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Training" = "#005030", "Testing" = "#FFB81C")) +
  labs(
    title = "Distribution of Monthly Spend: Training vs. Testing",
    x = "Monthly Spend ($)",
    y = "Density",
    fill = "Dataset"
  ) +
  theme_minimal()
```

```{r}
#| label: split-viz2
# Compare tenure distributions
bind_rows(
  customer_train |> mutate(set = "Training"),
  customer_test |> mutate(set = "Testing")
) |>
  ggplot(aes(x = tenure, fill = set)) +
  geom_histogram(alpha = 0.6, bins = 20, position = "identity") +
  scale_fill_manual(values = c("Training" = "#005030", "Testing" = "#FFB81C")) +
  labs(
    title = "Distribution of Tenure: Training vs. Testing",
    x = "Tenure (months)",
    y = "Count",
    fill = "Dataset"
  ) +
  theme_minimal()
```

## The validation set

Sometimes you want a **third** split — a validation set — for tuning hyperparameters without touching the test set:

```{r}
#| label: validation-split
set.seed(123)

# Three-way split: 60% train, 20% validation, 20% test
customer_val_split <- initial_validation_split(
  customer_data,
  prop = c(0.6, 0.2),
  strata = churn
)

customer_val_split
```

```{r}
#| label: validation-extract
train_val <- training(customer_val_split)
val_set <- validation(customer_val_split)
test_val <- testing(customer_val_split)

cat("Training:   ", nrow(train_val), "rows\n")
cat("Validation: ", nrow(val_set), "rows\n")
cat("Testing:    ", nrow(test_val), "rows\n")
```

::: callout-note
We will use **cross-validation** (TMWR Chapter 10) as a more efficient alternative to a separate validation set in later weeks.
:::

## ✏️ Practice 5.1 — Splitting your own data

Work through the following steps:

```{r}
#| label: practice-5-1a
# Step 1: Set a seed for reproducibility
set.seed(2024)

# Step 2: Create a stratified 80/20 split on churn
# YOUR CODE HERE
practice_split <- initial_split(customer_data, prop = 0.80, strata = churn)

# Step 3: Extract training and testing sets
practice_train <- training(practice_split)
practice_test <- testing(practice_split)

# Step 4: Verify the split sizes
cat("Training rows:", nrow(practice_train), "\n")
cat("Testing rows: ", nrow(practice_test), "\n")
```

```{r}
#| label: practice-5-1b
# Step 5: Verify churn rates are similar in both sets
practice_train |>
  count(churn) |>
  mutate(pct = round(n / sum(n) * 100, 1), 
         set = "Training") |>
  bind_rows(
    practice_test |>
      count(churn) |>
      mutate(pct = round(n / sum(n) * 100, 1), 
             set = "Testing")
  ) |>
  select(set, churn, n, pct)
```

```{r}
#| label: practice-5-1c
# Step 6: Compare distributions of a key predictor across splits
# Try changing 'last_login_days' to other variables
bind_rows(
  practice_train |> mutate(set = "Training"),
  practice_test |> mutate(set = "Testing")
) |>
  ggplot(aes(x = last_login_days, fill = set)) +
  geom_density(alpha = 0.5) +
  scale_fill_manual(values = c("Training" = "#005030", "Testing" = "#FFB81C")) +
  labs(
    title = "Distribution of Last Login Days: Training vs. Testing",
    x = "Days since last login",
    y = "Density",
    fill = "Dataset"
  ) +
  theme_minimal()
```

## ✏️ Practice 5.2 — What goes wrong without stratification?

This exercise illustrates the risk of imbalanced splits:

```{r}
#| label: practice-5-2
# Create a very small imbalanced dataset
set.seed(99)
small_imbalanced <- tibble(
  x = rnorm(200),
  target = factor(sample(
    c("rare", "common"),
    200,
    replace = TRUE,
    prob = c(0.05, 0.95)
  ))
)

cat("Full dataset class distribution:\n")
small_imbalanced |> count(target) |> mutate(pct = round(n / sum(n) * 100, 1))
```

```{r}
#| label: practice-5-2b
# Split WITHOUT stratification 10 times and record rare class % in test set
set.seed(1)
no_strata_results <- map_dfr(1:10, function(i) {
  sp <- initial_split(small_imbalanced, prop = 0.8)
  tibble(
    trial = i,
    pct_rare = mean(testing(sp)$target == "rare") * 100,
    stratified = "No"
  )
})

# Split WITH stratification 10 times
strata_results <- map_dfr(1:10, function(i) {
  sp <- initial_split(small_imbalanced, prop = 0.8, strata = target)
  tibble(
    trial = i,
    pct_rare = mean(testing(sp)$target == "rare") * 100,
    stratified = "Yes"
  )
})

bind_rows(no_strata_results, strata_results) |>
  ggplot(aes(x = factor(trial), y = pct_rare, fill = stratified)) +
  geom_col(position = "dodge") +
  geom_hline(yintercept = 5, linetype = "dashed", color = "gray40") +
  scale_fill_manual(values = c("No" = "#B52B4C", "Yes" = "#005030")) +
  labs(
    title = "% of Rare Class in Test Set Across 10 Splits",
    subtitle = "Dashed line = true proportion (5%). Stratified splits are more consistent.",
    x = "Trial",
    y = "% Rare class in test set",
    fill = "Stratified?"
  ) +
  theme_minimal()
```

::: callout-important
**Takeaway:** Without stratification, some test sets may have very few (or even zero) instances of the rare class. This makes performance estimates unreliable. Always stratify when classes are imbalanced.
:::

------------------------------------------------------------------------

# Putting It Together — A First End-to-End Example

Now let's combine everything from Chapters 1, 3, and 5 into a simple but complete modeling workflow. We will use the training data only for fitting and save the test set for the end.

## Step 1 — Split the data

```{r}
#| label: e2e-split
set.seed(123)

final_split <- initial_split(customer_data, prop = 0.80, strata = churn)
final_train <- training(final_split)
final_test <- testing(final_split)

cat("Training:", nrow(final_train), "rows\n")
cat("Testing: ", nrow(final_test), "rows\n")
```

## Step 2 — Explore the training data only

::: callout-warning
All exploratory analysis should use **training data only**. If you explore the test set and let that influence your modeling decisions, you are leaking information and your final performance estimate will be optimistic.
:::

```{r}
#| label: e2e-explore
# Churn rate by number of complaints
final_train |>
  group_by(num_complaints) |>
  summarise(
    n = n(),
    churn_rate = mean(churn == "yes") * 100
  ) |>
  filter(n >= 10)
```

```{r}
#| label: e2e-explore2
# Distribution of tenure by churn status
final_train |>
  ggplot(aes(x = tenure, fill = churn)) +
  geom_density(alpha = 0.6) +
  scale_fill_manual(values = c("no" = "#005030", "yes" = "#B52B4C")) +
  labs(
    title = "Tenure Distribution by Churn Status (Training Data)",
    x = "Tenure (months)",
    y = "Density",
    fill = "Churned?"
  ) +
  theme_minimal()
```

## Step 3 — Fit a model on training data

```{r}
#| label: e2e-fit
# Logistic regression using base R (we will use parsnip next week)
churn_fit <- glm(
  churn ~ tenure +
    monthly_spend +
    num_products +
    num_complaints +
    last_login_days,
  data = final_train,
  family = binomial
)

tidy(churn_fit)
```

```{r}
#| label: e2e-glance
glance(churn_fit)
```

## Step 4 — Evaluate on the test set (once!)

```{r}
#| label: e2e-evaluate
# Generate predictions on the test set
test_predictions <- augment(
  churn_fit,
  newdata = final_test,
  type.predict = "response"
) |>
  mutate(
    .pred_class = factor(ifelse(.fitted > 0.5, "yes", "no"))
  )

# Confusion matrix
conf_mat_result <- conf_mat(
  test_predictions,
  truth = churn,
  estimate = .pred_class
)

conf_mat_result
```

```{r}
#| label: e2e-metrics
# Accuracy
accuracy(test_predictions, truth = churn, estimate = .pred_class)
```

::: callout-note
We are using this simple threshold (0.5) for illustration. In later weeks we will learn how to choose thresholds based on marketing decision context and how to evaluate models more rigorously using resampling.
:::

------------------------------------------------------------------------

# Chapter Summaries

## Chapter 1 takeaways

-   Models can be **descriptive**, **inferential**, or **predictive** — know which type you need before you start
-   Good modeling software should be **consistent**, **safe**, and **expressive** — tidymodels is designed with these principles
-   Modeling is an **iterative process**, not a linear one

## Chapter 3 takeaways

-   The R formula interface (`~`) is powerful and expressive
-   Base R model output is hard to work with — `broom` functions (`tidy()`, `glance()`, `augment()`) solve this
-   tidymodels provides a **unified interface** across model types so you do not need to learn different syntax for every algorithm

## Chapter 5 takeaways

-   The **data budget**: every use of data for a decision "spends" some of its ability to give unbiased estimates
-   Always split into **training** and **testing** before any modeling
-   Use **stratified splits** when outcome classes are imbalanced
-   Never use the test set more than once — doing so leads to overfitting to the test data

------------------------------------------------------------------------

# Exercises

Complete these before the next class.

## Exercise 1 — Broom practice

Using the `customer_data` dataset (before splitting):

a.  Fit a linear regression predicting `monthly_spend` from `tenure`, `num_products`, and `region`
b.  Use `tidy()` to extract coefficients. Which predictors are significant at the 0.05 level?
c.  Use `glance()` to check R². Is the model a good fit?
d.  Use `augment()` and ggplot2 to create a residual plot. Do you see any patterns?

```{r}
#| label: exercise-1
#| eval: false
# YOUR CODE HERE
spend_model <- lm(___ ~ ___ + ___ + ___, data = customer_data)
tidy(___)
glance(___)
augment(___) |>
  ggplot(aes(x = ___, y = ___)) +
  geom_point()
```

## Exercise 2 — Data splitting

Using the `customer_data` dataset:

a.  Create a **70/30** stratified split on `churn`
b.  Verify that the churn rate is similar in both sets
c.  Check whether the distribution of `last_login_days` looks similar in training and testing

```{r}
#| label: exercise-2
#| eval: false
set.seed(456)

# YOUR CODE HERE
ex2_split <- initial_split(customer_data, prop = ___, strata = ___)
ex2_train <- training(___)
ex2_test <- testing(___)

# Verify churn rate
ex2_train |> count(___) |> mutate(pct = n / sum(n))
ex2_test |> count(___) |> mutate(pct = n / sum(n))
```

## Exercise 3 — Critical thinking

Answer the following in 2–3 sentences each:

a.  A colleague says: "I looked at the test set to understand the data better before modeling. I did not fit any models on it." Is this a problem? Why or why not?

b.  You are building a fraud detection model. Only 0.1% of transactions are fraudulent. Why is stratified splitting especially important here?

c.  A model achieves 92% accuracy on the training set and 61% accuracy on the test set. What does this tell you? What would you do next?

------------------------------------------------------------------------

# Resources

| Resource | Link |
|---------------------------------------------|---------------------------|
| Tidy Modeling with R (free) | [tmwr.org](https://www.tmwr.org) |
| tidymodels documentation | [tidymodels.org](https://www.tidymodels.org) |
| rsample reference | [rsample.tidymodels.org](https://rsample.tidymodels.org) |
| broom reference | [broom.tidymodels.org](https://broom.tidymodels.org) |
| R for Data Science | [r4ds.hadley.nz](https://r4ds.hadley.nz) |

------------------------------------------------------------------------

*IBM 6540 • Applied Machine Learning for Marketing with tidymodels • Cal Poly Pomona*